Data Cleaning logbook

### 2018-04-10 docs/data_cleaning_logbook.Rmd
Previous change slinked to cleaning notebook

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(between(abundancia, 0, 100)) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

write.csv(x = conapesca, file = here::here("data", "conapesca.csv"))

>>>>

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(between(abundancia, 0.1, 100)) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

write.csv(x = conapesca, file = here::here("data", "conapesca.csv"), row.names = F)
